---
title: "Simple document"
author: "Meghan"
output: html_document
html_document: true
---

I'm an R Markdown document! 

# Section 0: libraries
```{r load_libraries, message = F}
library(tidyverse)
```

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: tibble

```{r}
plot_df =
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1 + 2*x + rnorm(1000)
  )
```
# Section 4: ggplot

```{r}
ggplot(plot_df, aes (x = x)) + geom_histogram()
ggplot(plot_df, aes (x = x)) + geom_point()
```
# Section 5: Learning Assignment 2

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r learning_assessment_2}
library(tidyverse)

la_df =
  tibble(
    num_var = rnorm(n = 500, mean = 1),
    log_var = num_var > 0,
    abs_var = abs(num_var)
  )

ggplot(la_df, aes (x = abs_var)) + geom_histogram()

round(median(pull(la_df, num_var)),2)

```



text formatting
---------------------------------------------
*italic* or _italic_
**bold** or __bold__
`num_var`
superscript^2^ and subscript~2~

headings
---------------------------------------------
# 1st level header
## 2nd level
### 3rd level

# Section 7: Learning Assessment 3

After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.

* median: `r round(median(pull(la_df, num_var)),2)`
* mean: `r round(mean(pull(la_df, num_var)),2)`
* std: `r round(sd(pull(la_df, num_var)),2)`
